Syntax-Based Concept Alignment for Domain-Specific Machine Translation

### 2021-05-13 paper/paper.tex
changed plans for second ce experiment

We assess the correctness of the alignments the CE module is able to extract first from manually annotated data, then from the DMI and CSE corpus, comparing our results with those obtained with a standard statistical tool, \texttt{fast\_align} \cite{dyer-etal-2013-simple}.
Doing so requires manually labelling the correspondences as either correct or incorrect.

>>>>

We first assess the correctness of the alignments the CE module is able to extract from manually annotated data from the PUD treebanks, comparing our results with those obtained with a standard statistical tool, \texttt{fast\_align} \cite{dyer-etal-2013-simple}. 
In addition, we try to quantify the impact automatic parsing has on the performance of the CE module by comparing the above results wiht those obtained on the DMI and CSE corpora.
